Parsing Tweets into Universal Dependencies

### 2017-11-27 paper.tex
revise tokenization, add speed comparison, final evaluation comparison TBD.

\begin{document}
\maketitle
\begin{abstract}
We study the problem of analyzing tweets with
universal dependencies \citep[UD;][]{NIVRE16.348}. We extend the UD guidelines to cover
special constructions in tweets. Using the extended guidelines, we create
a new tweet treebank ({\sc Tweebank v2}), which has 55,607 tokens with
labeled attachments. 
It is more than four times larger than the (unlabeled) {\sc Tweebank
  v1} introduced by \citet{kong-EtAl:2014:EMNLP2014}. 
We characterize the disagreements
among our annotation and show that it is challenging to deliver
consistent annotation due to ambiguity in
understanding and explaining tweets. Using the new treebank,
we build a pipeline system to parse raw tweets into UD. To conquer the
annotation noise without sacrificing computational efficiency, we propose a new
method to distill an ensemble of 20 parsers into a single one. Our
parser achieves an improvement of 2.3 in LAS over \nascomment{which
  comparison is this?} the baseline
and outperforms parsers that are state-of-the-art on other treebanks.
\end{abstract}

\section{Introduction}
NLP for social media messages is challenging, both because domain
adaptation is required, but also because creating annotated datasets
(e.g., treebanks)
for training and evaluation is hard. 
Pioneering work by \citet{AAAIW113912} 
annotated 7,630 tokens' worth of tweets according to the
phrase-structure conventions of the Penn Treebank \citep[PTB]{Marcus93buildinga}.
Stanford dependencies were converted afterwards \nascomment{by who?}. 
\citet{kong-EtAl:2014:EMNLP2014} further studied the challenges in
annotating tweets and presented a tweet treebank ({\sc Tweebank}),
consisting of 12,149 tokens and largely following conventions
suggested by \citet{schneider-EtAl:2013:LAW7-ID}, fairly close to 
\citet{Yamada03statisticaldependency} dependencies (without labels). 
Both annotation efforts were highly influenced by the PTB, whose guidelines
have  good grammatical coverage on newswire. However, when it comes
to informal, unedited, user-generated text, the guidelines may leave
many annotation decisions unspecified.
%Motivation notes:  explain why UD is attractive (and more attractive
%than what previous work used, which was based on YM).  one reason is
%that it might allow sharing of texts annotated in different genres (or
%even languages, cite Waleed).  but universal annotation schemes are
%challenging!  this paper contends with the challenges of
%applying UD to social media texts.

@@

Universal dependencies \citep[UD]{NIVRE16.348} were introduced to enable
consistent annotation across different languages. To allow such
consistency, UD was designed to be adaptable to different genres and languages
\cite{guo-EtAl:2015:ACL-IJCNLP2,TACL892}. We propose that analyzing
the syntax of tweets can benefit from such adaptability. In this paper,
we introduce a new tweet treebank of 55,607 tokens that follows the UD
guidelines, but also contends with social media-specific challenges that were not
covered by UD guidelines. Our annotation includes 
tokenization, part-of-speech (POS) tags, and (labeled) universal dependencies.
We characterize the disagreement among our annotations and find that
consistent annotation is still challenging to deliver even with
the extended guidelines.

@@

Based on these annotations, we designed a pipeline to parse 
raw tweets into universal dependencies. Our pipeline includes: a
bidirectional LSTM (bi-LSTM) tokenizer, a word cluster-enhanced POS
tagger \citep[following][]{owoputi-EtAl:2013:NAACL-HLT}, and a stack LSTM parser
with character-based word representations
\cite{ballesteros-dyer-smith:2015:EMNLP}, which we refer to as our
``baseline'' parser.

To overcome the noise in our annotated data and achieve better performance
without sacrificing computational efficiency, we 
distill a 20-parser ensemble into a single greedy  parser 
\cite{DBLP:journals/corr/HintonVD15}.
We show further  that learning directly from the exploration of the ensemble parser
is more beneficial than learning from the gold standard ``oracle''
transition sequence. Experimental results show that an improvement of more
than 2.3 points \nascomment{again, not sure what this is quoting} in LAS over the baseline parser can be achieved with our
distillation method and that it outperforms other state-of-the-art parsers.

@@

\section{Annotation}\label{sec:anno}
\yicomment{Maybe we should contrast UD and kong's annotation strategy during each stage, because UD has also annotation guideline for every stage.}

@@

The regex-based tokenizer of \citet{ICWSM101540}---which was 
originally designed for an exploratory search interface called
TweetMotif, not for NLP---preserves most whitespace-delimited tokens, including 
hashtags, at-mentions, emoticons,  emojis, and unicode glyphs. 
They also treat contractions and acronyms as whole tokens and do not split them.
UD
tokenization,\footnote{\url{http://universaldependencies.org/u/overview/tokenization.html}}
in order to better serve dependency annotation, treats each syntactic word as token.
They therefore take a more aggressive strategy, including splitting
clitics from contractions or multiword expressions (e.g., {\it
  gonna}), and sometimes combining several orthographic tokens into a
single syntactic word. \yicomment{does UD support normalization for
  acronyms? Did not see it from website, need to check. related to
  ``idc''} \nascomment{unless we make a change, I think we need to say
  here that acronyms like \emph{idc} are left as a single token}

In our manual tokenization, we do not modify any non-informal \nascomment{is this defined?} token in tweets and leave them as in the original tweets. 
Then we mainly follow UD tokenization. We tokenize contractions and
multiword expressions into their syntactic components, but do not
combine tokens that appear as split in the original tweet.
For example, words like {\it gonna} or {\it can't} will be tokenized
to {\it gon na} and {\it ca n't}, and sequences like {\it Y O} and
{\it R E T W E E T} will be not combined back into single
words.\footnote{Such tokens only account for 0.067\%; we use the UD
  {\it goeswith} relation to resolve these cases in the syntax.}

@@

\paragraph{Acronym abbreviations.}  How should we syntactically
analyze acronym tokens like \emph{idc}
(abbreviating ``I don't care'') \yicomment{`idc' should be discussed in tokenization section, and actually it is already implied from POS section that it should be treated as a single word.}
 and \emph{rn} (``right now'')?  Should
they be decomposed into their component words, and if so should those
words be ``normalized'' into explicitly spelled out intermediate
forms? We follow \citet{kong-EtAl:2014:EMNLP2014} and annotate their
syntax as a single word without normalization. Their syntactic functions
are decided according to their context.\yicomment{again we should also mention UD tokenization, so might be worth adding a tokenization section}

\citet{eisenstein:2013:NAACL-HLT} studied the necessity of normalization
in social media text and argued that such normalization is problematic.
Our solution to the syntax of abbreviations follows the spirit of his argument. Because abbreviations which clearly carry
syntactic functions only constitute 0.06\% of the tokens in our
dataset, we believe that normalization is an unnecessarily complicated step.
% \nascomment{maybe we owe citations to
%   \cite{finin-EtAl:2010:MTURK,eisenstein:2013:NAACL-HLT} here?  maybe
%   better papers to cite}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth,trim={0 0 13cm 9cm},clip]{graphics/bilstm_tokenizer}
	\caption{The bi-LSTM tokenizer model that segments `its gonna be' into `it s gon na be'.}\label{fig:tok-model}
\end{figure}
We introduce a new
character-level bidirectional LSTM (bi-LSTM) sequence-labeling model
\cite{DBLP:journals/corr/HuangXY15,ma-hovy:2016:P16-1}
for tokenization.
Our model takes the raw sentence and tags each character in this 
sentence as whether it is the beginning of a word (1 as the beginning and 0 otherwise).
Figure \ref{fig:tok-model} shows our tokenization model.
Space is treated as an input but consistently assigned a special tag \$.

@@

\begin{table}[t]
	\centering
	\begin{tabular}{lr}
		\hline
		\it System & $F_1$ \\
		\hline
		  Stanford CoreNLP & 96.6 \\
		 Twokenizer & 94.4 \\
% 		UD pipe v1.2 & 94.7 \\
		UD pipe v1.2 & 97.3 \\
	 	our bi-LSTM tokenizer & \bf 98.3 \\
		\hline
	\end{tabular}
	\caption{Tokenizer comparison on the \textsc{Tweebank v2} test set.}\label{tbl:tok-result}
\end{table}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth,trim={0 0 13cm 3cm},clip]{graphics/bilstm_postagger}
	\caption{The bi-LSTM POS tagger model that tags `it s gon na be' as {\tt PRON AUX VERB PART AUX}.}\label{fig:pos-model}
	\yicomment{i'm a little confused by the pic, need discussion}
\end{figure}

@@

\begin{table}[t]
	\centering
	\begin{tabular}{rc}
		\hline
		\it System & $F_1$ \\
		\hline
		Stanford CoreNLP & 92.0 \\
		our tokenizer (\S\ref{sec:tok}) & 93.6 \\
		\hline
	\end{tabular}
	\caption{\citet{owoputi-EtAl:2013:NAACL-HLT} POS tagging performance with automatic tokenization on
          the \textsc{Tweebank v2} test set. \label{tbl:pos-result-vs-tok}}
\end{table}

@@

In our preliminary experiments, we train our parser on the combination of UD\_English
and \textsc{Tweebank v2} training sets. Gold-standard tokenization and automatic POS
tags are used. Automatic POS tags are assigned with 5-fold
jackknifing. Hyperparameters %, including the value of $\alpha$ in Equation \ref{eq:distill},
are tuned on the \textsc{Tweebank v2} development set. Unlabeled attachment score and
labeled attachment score (including punctuation) are reported.

\citet{reimers-gurevych:2017:EMNLP2017} and others have
pointed out that neural network training is 
nondeterministic and depends on the seed for the random
number generator.
Our preliminary experiments confirm this finding, with a gap of 1 LAS on development data
between the best (75.8) and worst (74.8) runs. To control for this
effect, we report the average of five differently-seeded runs, for
each model. \nascomment{please check! we did this for all systems,
  not just ours, right?}

@@

\begin{table}[t]
	\centering
	\begin{tabular}{rcc}
		\hline
		\it System & UAS & LAS \\
		\hline
		\citet{kong-EtAl:2014:EMNLP2014} &81.6 & 77.2 \\
		\citet{DBLP:journals/corr/DozatM16} & 81.9 &  77.7 \\
%		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 77.9 & 73.0 \\
		\newcite{ballesteros-EtAl:2016:EMNLP2016} & 80.4 & 75.8 \\
		\hdashline
		Ensemble (20) & 83.5 & 79.4 \\
		Distillation ($\alpha =1.0$) & 82.2 & 78.0 \\
		Distillation ($\alpha =0.9$) & 82.4 & 78.1 \\		
		Distillation with exploration & 82.5 & 78.4 \\
		\hline
	\end{tabular}
	\caption{Dependency parser comparison on \textsc{Tweebank v2},
           with automatic POS tags. \label{tbl:parse-result}}
\end{table}

\paragraph{Initial results.}  The first section of Table~\ref{tbl:parse-result} compares
the stack LSTM with {\sc TweeboParser} (the system 
of \citealp{kong-EtAl:2014:EMNLP2014}) and the state-of-the-art parser
in the CoNLL 2017 evaluations, due to
 \citet{DBLP:journals/corr/DozatM16}, both of which are graph-based
 parsers requiring superlinear runtime. \nascomment{can we quantify
   how much time each one takes, either in tweets parsed per second or
   seconds per tweet?}
Both of the comparison systems are re-trained on the same data as our
system.
Our system lags behind by nearly two LAS
points.

\paragraph{Ensemble.}  Due both to ambiguity in the training
data---which most loss functions are not robust to \citep{Frnay2014ClassificationIT}, including the log loss we use, following
\citet{ballesteros-dyer-smith:2015:EMNLP}---and due to the instability
of neural network training, we follow \citet{Dietterich2000} and
consider an ensemble of twenty parsers trained using different random
initialization.  To parse at test time, the transition probabilities of the twenty
members of the ensemble are averaged.  The result achieves LAS of
79.4, outperforming all three systems above (Table~\ref{tbl:parse-result}).

@@

Our approach follows \newcite{DBLP:journals/corr/HintonVD15}
and \newcite{kim-rush:2016:EMNLP2016}.  
Note that training a transition-based parser typically involves the
transformation of the training data into a sequence of ``oracle'' state-action
pairs.
Let $q(a \mid s)$ denote the distilled model's
probability of an action $a$ given parser state $s$; let $p(a \mid s)$ be the probability under the
ensemble (i.e., the average of the 20 separately-trained ensemble
members) \nascomment{check}.
To train the distilled model, we minimize the interpolation between
their distillation loss and the conventional log loss:
\begin{align}
\min_q \quad  & \alpha \sum_i \underbrace{\sum_{a} q(a \mid s_i) \cdot p(a
  \mid s_i)}_{\text{distillation loss}} \\
& +\ (1 - \alpha) \sum_i \underbrace{- \log q(a_i \mid
  s_i)}_{\text{log loss}} \nonumber
\end{align}

@@

\begin{table}[t]
	\centering
	\begin{tabular}{rcc}
		\hline
		\it System & UAS & LAS \\
		\hline
		\newcite{kuncoro-16} & 94.3 & 92.1 \\
		\citet{DBLP:journals/corr/DozatM16} & 95.7 & 94.1 \\
		\hdashline
		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 93.0 & 90.9 \\		
		%		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 77.9 & 73.0 \\
		Ensemble (20) & 94.5 & 92.6 \\
		Distillation ($\alpha =1.0$) & 93.8 & 91.7 \\
		Distillation with exploration  & 94.1 & 92.0 \\
		\hline
	\end{tabular}
	\caption{Dependency parser comparison on PTB test set.}\label{tbl:parse-result-PTB}
\end{table}

\nascomment{need to clarify:  is this UD?} We perform additional experiments on the Penn Treebank, following
the settings of \newcite{dyer-EtAl:2015:ACL-IJCNLP};
Table~\ref{tbl:parse-result-PTB} shows a similar trend, and we achieve
performance close to that of the graph-based parser of \citet{kuncoro-16}.
However, this greedy approach still lags behind the very strong
graph-based system of \citet{DBLP:journals/corr/DozatM16}.

\begin{table}[t]
	\centering
	\begin{tabular}{rc}
		\hline
		\it Pipeline & $F_1$\\
		\hline
		Tokenization & 98.3 \\		
		POS tagging & 93.7 \\
		Universal dependencies & 74.1 \\
		\hline
	\end{tabular}
	\caption{Evaluating our model in pipeline
          manner. \nascomment{should this be ``F1''?  shouldn't the
            last line be LAS?}\label{tbl:pipline} }
\end{table}

\paragraph{Pipeline evaluation.} Finally, we report  our full
pipeline's performance in  Table \ref{tbl:pipline}. We see the
importance of segmentation:  without gold segmentation, UD parsing
performance drops by more than four points.

>>>>

\begin{document}
\maketitle
\begin{abstract}
We study the problem of analyzing tweets with
universal dependencies \citep[UD;][]{NIVRE16.348}. We extend the UD guidelines to cover
special constructions in tweets. Using the extended guidelines, we create
a new tweet treebank ({\sc Tweebank v2}), which has 55,607 tokens with
labeled attachments. 
It is more than four times larger than the (unlabeled) {\sc Tweebank
  v1} introduced by \citet{kong-EtAl:2014:EMNLP2014}. 
We characterize the disagreements
among our annotation and show that it is challenging to deliver
consistent annotation due to ambiguity in
understanding and explaining tweets. Using the new treebank,
we build a pipeline system to parse raw tweets into UD. To overcome the
annotation noise without sacrificing computational efficiency, we propose a new
method to distill an ensemble of 20 transition-based parsers into a single one. Our
parser achieves an improvement of 2.3 in LAS over \nascomment{which
  comparison is this?} the singlely trained baseline
and outperforms parsers that are state-of-the-art on other treebanks.
\end{abstract}

\section{Introduction}
NLP for social media messages is challenging, both because domain
adaptation is required, but also because creating annotated datasets
(e.g., treebanks)
for training and evaluation is hard. 
Pioneering work by \citet{AAAIW113912} 
annotated 7,630 tokens' worth of tweets according to the
phrase-structure conventions of the Penn Treebank \citep[PTB]{Marcus93buildinga}.
Stanford dependencies were converted afterwards in their work  \nascomment{by who?}. 
\citet{kong-EtAl:2014:EMNLP2014} further studied the challenges in
annotating tweets and presented a tweet treebank ({\sc Tweebank}),
consisting of 12,149 tokens and largely following conventions
suggested by \citet{schneider-EtAl:2013:LAW7-ID}, fairly close to 
\citet{Yamada03statisticaldependency} dependencies (without labels). 
Both annotation efforts were highly influenced by the PTB, whose guidelines
have  good grammatical coverage on newswire. However, when it comes
to informal, unedited, user-generated text, the guidelines may leave
many annotation decisions unspecified.
%Motivation notes:  explain why UD is attractive (and more attractive
%than what previous work used, which was based on YM).  one reason is
%that it might allow sharing of texts annotated in different genres (or
%even languages, cite Waleed).  but universal annotation schemes are
%challenging!  this paper contends with the challenges of
%applying UD to social media texts.

@@

Universal dependencies \citep[UD]{NIVRE16.348} were introduced to enable
consistent annotation across different languages. To allow such
consistency, UD was designed to be adaptable to different genres \cite{wang-EtAl:2017:Long6} 
and languages \cite{guo-EtAl:2015:ACL-IJCNLP2,TACL892}. We propose that analyzing
the syntax of tweets can benefit from such adaptability. In this paper,
we introduce a new tweet treebank of 55,607 tokens that follows the UD
guidelines, but also contends with social media-specific challenges that were not
covered by UD guidelines. Our annotation includes 
tokenization, part-of-speech (POS) tags, and (labeled) universal dependencies.
We characterize the disagreement among our annotations and find that
consistent annotation is still challenging to deliver even with
the extended guidelines.

@@

Based on these annotations, we designed a pipeline to parse 
raw tweets into universal dependencies. Our pipeline includes: a
bidirectional LSTM (bi-LSTM) tokenizer, a word cluster-enhanced POS
tagger \citep[following][]{owoputi-EtAl:2013:NAACL-HLT}, and a stack LSTM parser
with character-based word representations
\cite{ballesteros-dyer-smith:2015:EMNLP}, which we refer to as our
``baseline'' parser.
To overcome the noise in our annotated data and achieve better performance
without sacrificing computational efficiency, we 
distill a 20-parser ensemble into a single greedy  parser 
\cite{DBLP:journals/corr/HintonVD15}.
We show further  that learning directly from the exploration of the ensemble parser
is more beneficial than learning from the gold standard ``oracle''
transition sequence. Experimental results show that an improvement of more
than 2.3 points \nascomment{again, not sure what this is quoting} in LAS over the baseline parser can be achieved with our
distillation method and that it outperforms other state-of-the-art parsers.

@@

\section{Annotation}\label{sec:anno}
%\yicomment{Maybe we should contrast UD and kong's annotation strategy during each stage, because UD has also annotation guideline for every stage.}

@@

The regex-based tokenizer of \citet{ICWSM101540}---which was 
originally designed for an exploratory search interface called
TweetMotif, not for NLP---preserves most whitespace-delimited tokens, including 
hashtags, at-mentions, emoticons, and unicode glyphs. 
They also treat contractions and acronyms as whole tokens and do not split them.
UD
tokenization,\footnote{\url{http://universaldependencies.org/u/overview/tokenization.html}}
in order to better serve dependency annotation, treats each syntactic word as token.
They therefore more aggressively split
clitics from contractions (e.g., {\it  gonna} is tokenized as {\it gon} and {\it na}; {\it its}
is tokenized as {\it it} and {\it s} when {\it s} is a copula). But acronyms is not touched
in the UD tokenization guidelines. Thus, we follow the UD tokenization for contractions
and left acronyms like {\em idc} as a single token.
\yicomment{does UD support normalization for
  acronyms? Did not see it from website, need to check. related to
  ``idc''} \nascomment{unless we make a change, I think we need to say
  here that acronyms like \emph{idc} are left as a single token}
\yjcomment{mentioned acronymns, we don't have the problem of normalization, cause
normalization was just annotated for data study.}

In the different direction of splitting tokens, UD guidelines also suggest to merge
{\it multi-token words} (e.g. {\it 20 000}) into one single token in some special
cases. We witnessed a small number of tweets that contain mult-token words
(e.g. {\it Y O}, and {\it R E T W E E T}) but didn't combine them due to simplification.
Such tokens only account for 0.067\% and we use the UD
  {\it goeswith} relation to resolve these cases in the dependency annotations.

@@

\paragraph{Acronym abbreviations.}  How should we syntactically
analyze acronym tokens like \emph{idc}
(abbreviating ``I don't care'')
 and \emph{rn} (``right now'')?  Should
they be decomposed into their component words, and if so should those
words be ``normalized'' into explicitly spelled out intermediate
forms? We follow \citet{kong-EtAl:2014:EMNLP2014} and annotate their
syntax as a single word without normalization. Their syntactic functions
are decided according to their context. \citet{eisenstein:2013:NAACL-HLT} studied the necessity of normalization
in social media text and argued that such normalization is problematic.
Our solution to the syntax of abbreviations follows the spirit of his argument. Because abbreviations which clearly carry
syntactic functions only constitute 0.06\% of the tokens in our
dataset, we believe that normalization is an unnecessarily complicated step.
% \nascomment{maybe we owe citations to
%   \cite{finin-EtAl:2010:MTURK,eisenstein:2013:NAACL-HLT} here?  maybe
%   better papers to cite}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth,trim={0 0 11cm 9cm},clip]{graphics/bilstm_tokenizer}
	\caption{The bi-LSTM tokenizer model that segments `its gonna be' into `it s gon na be'.}\label{fig:tok-model}
\end{figure}
We introduce a new
character-level bidirectional LSTM (bi-LSTM) sequence-labeling model
\cite{DBLP:journals/corr/HuangXY15,ma-hovy:2016:P16-1}
for tokenization.
Our model takes the raw sentence and tags each character in this 
sentence as whether it is the beginning of a word (1 as the beginning and 0 otherwise).
Figure \ref{fig:tok-model} shows our tokenization model.
Space is treated as an input but consistently assigned a special tag \$.

@@

\begin{table}[t]
	\centering
	\begin{tabular}{lr}
		\hline
		\it System & \it F1 \\
		\hline
		  Stanford CoreNLP & 96.6 \\
		 Twokenizer & 94.4 \\
% 		UD pipe v1.2 & 94.7 \\
		UD pipe v1.2 & 97.3 \\
	 	our bi-LSTM tokenizer & \bf 98.3 \\
		\hline
	\end{tabular}
	\caption{Tokenizer comparison on the \textsc{Tweebank v2} test set.}\label{tbl:tok-result}
\end{table}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth,trim={0 0 11cm 3cm},clip]{graphics/bilstm_postagger}
	\caption{The bi-LSTM POS tagger model that tags `it s gon na be' as {\tt PRON AUX VERB PART AUX}.}\label{fig:pos-model}
	%\yicomment{i'm a little confused by the pic, need discussion}
\end{figure}

@@

\begin{table}[t]
	\centering
	\begin{tabular}{rc}
		\hline
		\it System & \it F1 \\
		\hline
		Stanford CoreNLP & 92.0 \\
		our tokenizer (\S\ref{sec:tok}) & 93.6 \\
		\hline
	\end{tabular}
	\caption{\citet{owoputi-EtAl:2013:NAACL-HLT} POS tagging performance with automatic tokenization on
          the \textsc{Tweebank v2} test set. \label{tbl:pos-result-vs-tok}}
\end{table}

@@

In our preliminary experiments, we train our parser on the combination of UD\_English
and \textsc{Tweebank v2} training sets. Gold-standard tokenization and automatic POS
tags are used. Automatic POS tags are assigned with 5-fold
jackknifing. Hyperparameters %, including the value of $\alpha$ in Equation \ref{eq:distill},
are tuned on the \textsc{Tweebank v2} development set. Unlabeled attachment score and
labeled attachment score (including punctuation) are reported.
All the experiments were ran on a Xeon E5-2670 2.6 GHz machine.

\citet{reimers-gurevych:2017:EMNLP2017} and others have
pointed out that neural network training is 
nondeterministic and depends on the seed for the random
number generator.
Our preliminary experiments confirm this finding, with a gap of 1 LAS on development data
between the best (75.8) and worst (74.8) runs. To control for this
effect, we report the average of five differently-seeded runs, for
each model and the compared one. %\nascomment{please check! we did this for all systems,
%  not just ours, right?}

@@

\begin{table}[t]
	\centering
	\begin{tabular}{rccc}
		\hline
		\it System & UAS & LAS & SP \\
		\hline
		\citet{kong-EtAl:2014:EMNLP2014} &81.6 & 77.2 & 0.3 \\
		\citet{DBLP:journals/corr/DozatM16} & 81.9 &  77.7 & 1.7 \\
%		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 77.9 & 73.0 \\
		\newcite{ballesteros-EtAl:2016:EMNLP2016} & 80.4 & 75.8 & 2.3 \\
		\hdashline
		Ensemble (20) & 83.5 & 79.4 & 0.2 \\
		Distillation ($\alpha =1.0$) & 82.2 & 78.0 & 2.3 \\
		Distillation ($\alpha =0.9$) & 82.4 & 78.1 & 2.3 \\		
		Distillation w/ exploration & 82.5 & 78.4 & 2.3 \\
		\hline
	\end{tabular}
	\caption{Dependency parser comparison on \textsc{Tweebank v2},
           with automatic POS tags. The {\it SP} column shows
           the parsing speed evaluated by the number of thousand tokens
           the model processed per second. For fair comparison, we limit the
           number of CPU used in \citet{DBLP:journals/corr/DozatM16} experiments to 1.
            \label{tbl:parse-result}}
\end{table}

\paragraph{Initial results.}  The first section of Table~\ref{tbl:parse-result} compares
the stack LSTM with {\sc TweeboParser} (the system 
of \citealp{kong-EtAl:2014:EMNLP2014}) and the state-of-the-art parser
in the CoNLL 2017 evaluations, due to
 \citet{DBLP:journals/corr/DozatM16}, both of which are graph-based
 parsers requiring superlinear runtime. %\nascomment{can we quantify
%   how much time each one takes, either in tweets parsed per second or
%   seconds per tweet?}
Both of the comparison systems are re-trained on the same data as our
system.
Our system lags behind by nearly two LAS
points but runs faster than both of them.

\begin{table*}[t]
	\centering
	\begin{tabular}{rrcc}
		\hline
		\it Pipeline & Metrics & Our & SOTA stack\\
		\hline
		Tokenization & \it F1 & 98.3 & \\		
		POS tagging &  \it Precision F1 & 93.7 & \\
		Universal dependencies & \it LAS F1 & 74.1 & \\
		\hline
	\end{tabular}
	\caption{Evaluating our model in pipeline
		manner. \nascomment{should this be ``F1''?  shouldn't the
			last line be LAS?}\label{tbl:pipline} }
\end{table*}

\paragraph{Ensemble.}  Due both to ambiguity in the training
data---which most loss functions are not robust to \citep{Frnay2014ClassificationIT}, including the log loss we use, following
\citet{ballesteros-dyer-smith:2015:EMNLP}---and due to the instability
of neural network training, we follow \citet{Dietterich2000} and
consider an ensemble of twenty parsers trained using different random
initialization.  To parse at test time, the transition probabilities of the twenty
members of the ensemble are averaged.  The result achieves LAS of
79.4, outperforming all three systems above (Table~\ref{tbl:parse-result}).
However, ensembling 20 parsers also significantly slows down the parsing
speed and leads to the slowest system in our comparison.

@@

Our approach follows \newcite{DBLP:journals/corr/HintonVD15}
and \newcite{kim-rush:2016:EMNLP2016}.  
Note that training a transition-based parser typically involves the
transformation of the training data into a sequence of ``oracle'' state-action
pairs.
Let $q(a \mid s)$ denote the distilled model's
probability of an action $a$ given parser state $s$; let $p(a \mid s)$ be the probability under the
ensemble (i.e., the average of the 20 separately-trained ensemble
members) \nascomment{check} \yjcomment{checked}.
To train the distilled model, we minimize the interpolation between
their distillation loss and the conventional log loss:
\begin{align}
{\arg\,\min}_q \quad  & \alpha \sum_i \underbrace{\sum_{a} q(a \mid s_i) \cdot p(a
  \mid s_i)}_{\text{distillation loss}} \\
& +\ (1 - \alpha) \sum_i \underbrace{- \log q(a_i \mid
  s_i)}_{\text{log loss}} \nonumber
\end{align}

@@

%
%\begin{table}[t]
%	\centering
%	\begin{tabular}{rcc}
%		\hline
%		\it System & UAS & LAS \\
%		\hline
%		\newcite{kuncoro-16} & 94.3 & 92.1 \\
%		\citet{DBLP:journals/corr/DozatM16} & 95.7 & 94.1 \\
%		\hdashline
%		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 93.0 & 90.9 \\		
%		%		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 77.9 & 73.0 \\
%		Ensemble (20) & 94.5 & 92.6 \\
%		Distillation ($\alpha =1.0$) & 93.8 & 91.7 \\
%		Distillation with exploration  & 94.1 & 92.0 \\
%		\hline
%	\end{tabular}
%	\caption{Dependency parser comparison on PTB test set.}\label{tbl:parse-result-PTB}
%\end{table}

%\nascomment{need to clarify:  is this UD?} We perform additional experiments on the Penn Treebank, following
%the settings of \newcite{dyer-EtAl:2015:ACL-IJCNLP};
%Table~\ref{tbl:parse-result-PTB} shows a similar trend, and we achieve
%performance close to that of the graph-based parser of \citet{kuncoro-16}.
%However, this greedy approach still lags behind the very strong
%graph-based system of \citet{DBLP:journals/corr/DozatM16}.

\paragraph{Pipeline evaluation.} Finally, we report  our full
pipeline's performance in  Table \ref{tbl:pipline}.
We see the
importance of segmentation:  without gold segmentation, UD parsing
performance drops by more than four points. We also compare
our model with a stack of the state-of-the-art system: Stanford Tokenizer,
ARK tagger, and \citet{DBLP:journals/corr/DozatM16}'s parser. \yjcomment{tbd}
